\Trill: Secure firewall-traversing networking

### 2012-12-14 6.858/paper/paper.tex
Establishing trust

\documentclass[11pt]{article}

\usepackage{fancyhdr, geometry, hyperref, sectsty, titlesec, xspace}
\usepackage[parfill]{parskip}

@@

\sectionfont{\vspace{-2pt}\large}
\subsectionfont{\vspace{-2pt}\normalsize}
\subsubsectionfont{\normalfont\itshape}

\titlespacing\section{0pt}{10pt}{2pt}
\titlespacing\subsection{0pt}{8pt}{0pt}

\fancyhead[RO]{Carl Jackson \& Max Wang}
\fancyhead[LO]{\url{http://github.com/motmotchat/trill}}

\newcommand{\Trill}{\textsc{Trill}\xspace}
\newcommand{\Plume}{\textsc{Plume}\xspace}

\title{\Trill: Secure firewall-traversing networking}
\author{Carl Jackson \and Max Wang}
\date{December 14, 2012}

@@

We implemented \Trill, a networking abstraction that provides secure
communication between federated identities, either of which could be behind a
firewall.

\section{Design}

\subsection{Security}
The security of our system is based on standard cryptographic infrastructure and
libraries. By ``identities,'' we mean public key pairs, the private half of
which is uniquely known by an individual. This identity can be given one or more
names by means of X.509 certificates, and standard mechanisms like TLS allow
owners of identities to securely establish a communication channel and mutually
verify the other's identity.

@@

\subsection{Firewall Traversal}
Due to restrictions on many firewalls and NATs in place on the Internet, it is
impossible for arbitrary clients on the internet to establish peer-to-peer
communication. There are techniques for firewall/NAT traversal which involve
``tricking'' the networking layer into establishing a connection. We implemented
something similar to \texttt{chownat} (\url{http://samy.pl/chownat/}) in \Trill,
which appears to be a standard way to do this.

\section{Implementation}
% trill - client library. allows plug-and-play event loops, architected to (one
%   day!) support multiple TLS libraries.
% plume - server. separate login and protocol servers. access to domain root
%   keys has very small surface area. chroot more!

\subsection{Trill client library}

\subsection{Plume server}

>>>>

\documentclass[12pt]{article}

\usepackage{fancyhdr, geometry, hyperref, xspace}
\usepackage[parfill]{parskip}

@@

\fancyhead[RO]{Carl Jackson and Max Wang}
\fancyhead[LO]{\url{http://github.com/motmotchat/trill}}

\newcommand{\Trill}{\textsc{Trill}\xspace}

\title{\Trill: Secure firewall-traversing networking}
\author{Carl Jackson and Max Wang}
\date{December 14, 2012}

\makeatletter
\renewcommand{\maketitle}{%
  \thispagestyle{plain}%
  \begin{center}%
    {\LARGE \@title \par}%
    {\large \@author \par}%
    {\large \@date \par}%
  \end{center}%
}
\makeatother

@@

\section*{Overview}
We implemented \Trill, a networking abstraction that provides secure
communication between federated identities, either of which could be behind a
firewall.

\section*{Security}
The security of our system is based on standard cryptographic infrastructure and
libraries. By ``identities,'' we mean public key pairs, the private half of
which is uniquely known by an individual. This identity can be given one or more
names by means of X.509 certificates, and standard mechanisms like TLS allow
owners of identities to securely establish a communication channel and mutually
verify the other's identity.

@@

\section*{Firewall Traversal}
Due to restrictions on many firewalls and NATs in place on the Internet, it is
impossible for arbitrary clients on the internet to establish peer-to-peer
communication. There are techniques for firewall/NAT traversal which involve
``tricking'' the networking layer into establishing a connection. We implemented
something similar to \texttt{chownat} (\url{http://samy.pl/chownat/}) in \Trill,
which appears to be a standard way to do this.

\section*{Implementation}
% trill - client library. allows plug-and-play event loops, architected to (one
%   day!) support multiple TLS libraries.
% plume - server. separate login and protocol servers. access to domain root
%   keys has very small surface area. chroot more!
